Fast, Scalable Phrase-Based SMT Decoding

### 2016-02-08 acl.2016/acl2016.tex
acl paper

We will focus on two main optimizations that differs from the current Probing phrase-table implementation and that have application to other implementations. Firstly, we will look at the \textbf{caching} of often used translation rules. The default caching framework save the most recently looked up rules. However, this caching mechanism is actually slower than re-querying the phrase-table, Table~\ref{???}. We shall explore a simpler caching mechanism that creates the cache at the start of decoding and remain static thereafter.

>>>>

We will focus on two main optimizations that differs from the current Probing phrase-table implementation and that have application to other implementations. Firstly, we will look at the \textbf{caching} of often used translation rules. The default caching framework save the most recently looked up rules. However, this caching mechanism is actually slower than re-querying the phrase-table, Table~\ref{tab:phrase-table-cache}. 
\begin{table}[h]
\small
\begin{center}
\begin{tabular}{|l|c|c|} \hline
		& No cache	& Caching \\ \hline
Decoding time  	& 2032 		& 2302 \\ \hline
\end{tabular}
\end{center}
\caption{Decoding time (in sec with 32 threads) when using phrase-table cache}
\label{tab:phrase-table-cache}
\end{table}
We shall explore a simpler caching mechanism that creates the cache at the start of decoding and remain static thereafter.
